### 2023-12-17 sections/4-results.tex
lfd figures in place, also 2 more scaling dummies

@@

\begin{figure}
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}\\
\subcaption{Fashion-mnist for $k=10$.}
\label{fig:results:fashion-mnist-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}\\
\subcaption{Glove-25 for $k=10$.  }
\label{fig:results:glove-25-scaling}
\end{subfigure}%
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}\\
\subcaption{Sift for $k=10$.    }
\label{fig:results:sift-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/random-1000000-128-knn-10.png}\\
\subcaption{A random dataset for $k=10$.
}
\label{fig:results:random-scaling}
\end{subfigure}%

\caption{Algorithm performance across four datasets. In each plot, the horizontal axis represents increasing cardinality (size) of the dataset, while the vertical axis represents the throughput in queries per second (higher is better). TODO say something about plots that didn't finish.}
\end{figure}

>>>>

Figures~\ref{fig:results:fashion-mnist-lfd} show the local fractal dimension of.... (TODO fill this in)

%% LFD plots

\begin{figure}
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/fashion-mnist-60000-lfd.png}\\
\subcaption{Fashion-mnist}
\label{fig:results:fashion-mnist-lfd}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/glove-25-1183514-lfd.png}\\
\subcaption{Glove-25}
\label{fig:results:glove-25-lfd}
\end{subfigure}
\vspace{1em}
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/sift-1000000-lfd.png}\\
\subcaption{Sift}
\label{fig:results:sift-lfd}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/random-1000000-128-1000000-lfd.png}\\
\subcaption{A random dataset}
\label{fig:results:random-lfd}
\end{subfigure}
\vspace{1em}
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/silva-2224640-lfd.png}\\
\subcaption{Silva 18S metagenomics}
\label{fig:results:silva-lfd}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/radioml-97920-lfd.png}\\
\subcaption{RadioML}
\label{fig:results:radioml-lfd}
\end{subfigure}%

\caption{Local fractal dimension vs. cluster depth, grouped by decile of LFD, across six datasets.}
\end{figure}
%% end LFD plots

@@

\begin{figure}
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}
\subcaption{Fashion-mnist for $k=10$.}
\label{fig:results:fashion-mnist-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}
\subcaption{Glove-25 for $k=10$.  }
\label{fig:results:glove-25-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}
\subcaption{Sift for $k=10$.    }
\label{fig:results:sift-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/random-1000000-128-knn-10.png}
\subcaption{A random dataset for $k=10$.
}
\label{fig:results:random-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/silva-knn-10.png}
\subcaption{Silva for $k=10$.    }
\label{fig:results:silva-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/radioml-knn-10.png}
\subcaption{RadioML for $k=10$.
}
\label{fig:results:radioml-scaling}
\end{subfigure}%

\caption{Algorithm performance across six datasets, including a randomly-generated dataset. In each plot, the horizontal axis represents increasing cardinality (size) of the dataset, while the vertical axis represents the throughput in queries per second (higher is better). TODO say something about plots that didn't finish.}
\end{figure}
